---
title: "Audience response: motivation"
author: "Emma Rand"
output:
  html_document: bookdown::html_document2
  pdf_document: bookdown::pdf_document2
  word_document: default
bibliography: references.bib
figsintext: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.show = "asis")
```

```{r pkg}
# pkg
library(tidyverse)
library(likert)
library(psych)
library(gridExtra)
library(kableExtra)
library(jpeg)
library(png)
library(grid)
```



The importance placed on data handling and analysis in a biology degree can therefore come as surprise and not a welcome one! These subjects are recognised as among the more difficult to teach [e.g., @Du_Boulay1986], require more and harder work from the student and may be relatively unpopular [e.g., @Uttl2017-tk]. 
At the start of the first lecture of Data Analysis in R, I ask students to indicate the extent to which they agree with the statement "I will enjoy data analysis" and "How do you feel about R?"
 



```{r create}
r_feel <- data.frame(q1 = rep(c("Excited",
                                                          "Seems ok",
                                                          "Undecided",
                                                          "A bit\nworried",
                                                          "Terrified"), 
                                                        times = c(4, 19, 10, 34, 33)))

enjoy <- data.frame(q1 = rep(c("Definitely\nagree",
                                                       "Probably\nagree",
                                                       "Neutral",
                                                       "Probably\ndisagree",
                                                       "Definitely\ndisagree"), 
                                                     times = c(2, 9, 13, 43, 12)))
enjoy <- enjoy %>% 
  mutate("I will enjoy data analysis" = factor(q1, 
                                               levels = c("Definitely\ndisagree",
                                                          "Probably\ndisagree",
                                                          "Neutral",
                                                          "Probably\nagree",
                                                          "Definitely\nagree")))
r_feel <- r_feel %>% 
  mutate("How do you feel about R?" = factor(q1, 
                                             levels = c("Terrified",
                                                        "A bit\nworried",
                                                        "Undecided",
                                                        "Seems ok",
                                                        "Excited")))

```

```{r enjoy-figure}
lik <- likert(enjoy[2])
plota <- plot(lik,
              legend.position = "top",
              legend = "",
              text.size = 4,
              low.color = "lightblue",
              high.col = "lightgreen")
```

```{r feel-figure}
lik <- likert(r_feel[2])
plotb <- plot(lik,
              legend.position = "top",
              legend = "",
              text.size = 4,
              low.color = "lightblue",
              high.col = "lightgreen")
```



```{r comp-fig, fig.cap="Expectations of Stage 1 Biologists about of Data Analysis in 2018. Responses to the question '**I will enjoy data analysis**' (upper figure) and '**How do you feel about R?**' (lower figure).", fig.pos = 'h'}

grid.arrange(plota, plotb)


```



